---
title: "Rworksheet_Delgado#5"
author: "JR Delgado"
date: "2022-11-23"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
\hfill\break
Worksheet-5 in R
Worksheet for R Programming
\hfill\break
1. The table shows the enrollment of BS in Computer Science, SY 2010-2011.
a. Plot the data using a bar graph. Write the codes and copy the result.

```{r, error=TRUE}
students <- data.frame("Course Year" = c ("1st", "2nd", "3rd", "4th"), " 2019–2020" = c(80, 75, 70, 60))
students
```

```{r, error=TRUE}
course <- c(80,75,70,60)
bplot <- barplot(course, ylab = , names.arg = c("1st", "2nd", "3rd","4th"))
```

\hfill\break
b. Using the same table, label the barchart with
Title = ” Enrollment of BS Computer Science
horizontal axis = “Curriculum Year” and
vertical axis = “number of students”

```{r, error=TRUE}
bar2 <- barplot(course, col = rainbow(4),  
                main = " Enrollment of BS Computer Science",
                xlab = "Curriculum Year",
                ylab =  "Number of students", names.arg = c("1st", "2nd", "3rd","4th"))
bar2
```

\hfill\break
2. The monthly income of De Jesus family was spent on the following:
 60% on Food, 10% on electricity, 5% for savings, and
 25% for other miscellaneous expenses.

```{r, error=TRUE}
family_spent <- c(60,10,5,25) 
```

\hfill\break
a. Create a table for the above scenario. Write the codes and its result.

```{r, error=TRUE}
month_exp <- data.frame(
  exp_names = c("Food", "Electricity", "Savings", "Miscellaneous_expenses"),
  spent = c(60, 10, 5, 25)
)
month_exp
```


\hfill\break
b. Plot the data using a pie chart. Add labels, colors and legend.
 Write the codes and its result.

```{r, error=TRUE}
pie(family_spent, col = rainbow(4))
```


```{r, error=TRUE}
family_spent_labels <- round(family_spent/sum(family_spent) * 100, 10)
family_spent_labels <- paste(family_spent_labels, "%", sep = "")
```


```{r, error=TRUE}
pie1 <- pie(family_spent, main = "Expenses", col = rainbow(length(family_spent)), labels = family_spent_labels, cex= 0.8)

legend(1.5, 0.5, c(" Food", "Electricity","Savings","Other expenses"), cex= 0.6, bty = "n", fill = rainbow(length(family_spent)) )
```


\hfill\break
3. Open the mtcars dataset.

```{r, error=TRUE}
View(mtcars)
```


\hfill\break
a. Create a simple histogram specifically for mpg (miles per gallon) variable.
Use $ to select the mpg only. Write the codes and its result.

```{r, error=TRUE}
mtcarsData <- mtcars$mpg
mtcarsData

x <- hist(mtcarsData, col = "skyblue")
x
```


\hfill\break
b. Colored histogram with different number of bins.
 hist(mtcars$mpg, breaks=12, col="red")
 Note: breaks= controls the number of bins

```{r, error=TRUE}
hist(mtcarsData, breaks=5, col="red")
```

\hfill\break
c. Add a Normal Curve
x <- mtcars$mpg
h<-hist(x, breaks=10, col="red", xlab="Miles Per Gallon",
       main="Histogram with Normal Curve")
xfit<-seq(min(x),max(x),length=40)
yfit<-dnorm(xfit,mean=mean(x),sd=sd(x))
yfit <- yfit*diff(h$mids[1:2])*length(x)
lines(xfit, yfit, col="blue", lwd=2)
Copy the result.

```{r, error=TRUE}
curveData <- mtcarsData
curveData
```

```{r, error=TRUE}
histData <-hist(curveData, breaks=10, col="red", xlab="Miles Per Gallon",
                 main="Histogram with Normal Curve")
xfit<-seq(min(curveData),max(curveData),length=40)
yfit<-dnorm(xfit,mean=mean(curveData),sd=sd(curveData))
yfit <- yfit*diff(histData$mids[1:2])*length(curveData)
lines(xfit, yfit, col="blue", lwd=2)
histData
```

\hfill\break
4. Open the iris dataset. Create a subset for each species.
 a. Write the codes and its result.
 
```{r, error=TRUE}
View("iris")
```

```{r, error=TRUE}
data_iris <- data.frame(iris)
data_iris
```

```{r, error=TRUE}
data_setosa <- subset(data_iris, Species == 'setosa' )
data_setosa
```

```{r, error=TRUE}
data_versicolor <- subset(data_iris, Species == 'versicolor' )
data_versicolor
```

```{r, error=TRUE}
data_virgica <- subset(data_iris, Species == 'virginica' )
data_virgica
```


\hfill\break
b. Get the mean for every characteristics of each species using colMeans(). 
 Write the codes and its result. Example: setosa <- colMeans(setosa[sapply(setosaDF,is.numeric)])

```{r, error=TRUE}
setosa <- colMeans(data_setosa[sapply(data_setosa,is.numeric)])
setosa
```

```{r, error=TRUE}
versicolor <- colMeans(data_versicolor[sapply(data_versicolor,is.numeric)])
versicolor
```

```{r, error=TRUE}
virginica <- colMeans(data_virgica[sapply(data_virgica,is.numeric)])
virginica
```


\hfill\break
c. Combine all species by using rbind() The table should be look like this:
  

```{r, error=TRUE}  
combinedata <- rbind(setosa, versicolor,virginica)
combinedata
```

```{r, error=TRUE}
combineDF <- data.frame(combinedata)
combineDF
```

\hfill\break
d  From the data in 4-c: Create the barplot(). Write the codes and its result. The barplot should be like this.

```{r, error=TRUE}
barplot (as.matrix(combineDF), col = rainbow(3), main = "Iris Data",
         ylab = "Mean Scores",
         beside = T)
```
