---
title: "Rworksheet_Delgado#6"
author: "JR Delgado"
date: "2022-11-25"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


\hfill\break\
Worksheet-6
Worksheet for R Programming
----------------------------------------------------------------------------------------
```{r, error=TRUE}

library(dplyr)
library(ggplot2)

mpg1 <- as.data.frame(mpg)
mpg1
```

\hfill\break
1. How many columns are in mpg dataset? How about the number of rows? Show the codes and its result.
answer - it has 11 columns and a rows of 234

```{r, error=TRUE}
mpg_data <- glimpse(mpg1)
mpg_data 
```

\hfill\break
2. Which manufacturer has the most models in this data set? Which model has the most variations? 
answer: Dodge, it has 37 models.

```{r, error=TRUE}
most_model <- mpg_data %>% 
  group_by(manufacturer, model) %>% tally(sort = TRUE)
most_model
```

\hfill\break
a. Group the manufacturers and find the unique models. Copy the codes and result.


```{r, error=TRUE}
unique_model <- mpg_data %>% group_by(manufacturer,model) %>% 
  distinct(model) %>% count()
unique_model

colnames(unique_model) <- c("Manufacturer", "Model","Counts")
unique_model
```
\hfill\break
b. Graph the result by using plot() and ggplot(). Write the codes and its result.

```{r, error=TRUE}
plot(most_model)

ggplot(most_model, aes( manufacturer,model)) + geom_point()
```

\hfill\break
3. Same dataset will be used. You are going to show the relationship of the modeland the manufacturer.
a. What does ggplot(mpg, aes(model, manufacturer)) + geom_point() show? The data shows the manufacturer and model in a very understanding way of using a graphics plot

```{r, error=TRUE}
ggplot(mpg1, aes(model, manufacturer)) + geom_point()
```

\hfill\break
b. For you, is it useful? If not, how could you modify the data to make it more informative?
answer -  adding a legend to easily find the data.

\hfill\break
4. Using the pipe (%>%), group the model and get the number of cars per model. Show codes and its result.

```{r, error=TRUE}
cars_model <- mpg_data %>% group_by(model) %>% count()
cars_model

colnames(cars_model) <- c("Model","Counts")
```

\hfill\break
a. Plot using the geom_bar() + coord_flip() just like what is shown below. Show codes and its result.

```{r, error=TRUE}
qplot(model,data = mpg1, 
      main = "Number of Cars per Model",
      xlab = "Model",
      ylab = "Number of Cars", geom = "bar", fill = manufacturer) + coord_flip()
```

b. Use only the top 20 observations. Show code and results.

\hfill\break
```{r,error=TRUE}
top <- cars_model[1:20,] %>% top_n(2)
top

ggplot(top,aes(x = Model, y = Counts)) + 
  geom_bar(stat = "Identity") +coord_flip()
```

\hfill\break
5. Plot the relationship between cyl - number of cylinders and displ - engine displacement using geom_point with aesthetic colour = engine 
displacement. Title should be “Relationship between No. of Cylinders and Engine Displacement”.

\hfill\break
a. Show the codes and its result.

```{r, error=TRUE}
ggplot(data = mpg_data , mapping = aes(x = displ, y = cyl, main = "Relationship 
                                    between No of Cylinders and 
                                    Engine Displacement")) + 
  geom_point(mapping=aes(colour = "engine displacement")) 

```

\hfill\break
b. How would you describe its relationship?
answer - the scatter plot shows that the cyl is in  vertical lines(y-axis) and the displ are in  in horizontal lines(x-axis).
To easily locate the clustered data, just one look we can figure out wheres the Engine Displacement is. By having the engine displacement name in right middle side.


\hfill\break
6. Get the total number of observations for drv - type of drive train (f = front-wheel drive,
r = rear wheel drive, 4 = 4wd) and class - type of class (Example: suv, 2seater, etc.).

Plot using the geom_tile() where the number of observations for class be used as a fill for aesthetics.
\hfill\break
a. Show the codes and its result for the narrative in #6.

```{r, error=TRUE}
ggplot(data = mpg_data, mapping = aes(x = drv, y = class)) +
  geom_tile(aes(fill=class))
```

\hfill\break
b. Interpret the result.
answer - by mapping a geometric tile, the geom_title was shown in a diffrent colors, 
the drv are in the X axis while the class are in the Y axis.
\hfill\break
7. Discuss the difference between these codes. Its outputs for each are shown below.
answer - the graph are almost the same 
but the first code the colour blue ignore while in the second code the colour blue displayed. The r studio are t00 much sensitive in placing a proper code in the source code.
first code

```{r, error=TRUE}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy, colour = "blue"))
```

second code

```{r, error=TRUE}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy), colour = "blue")
```


\hfill\break
8. Try to run the command ?mpg. What is the result of this command?
answer - the result are in the help option, it shows the description for the data set of mpg.

```{r, error=TRUE}
?mpg
```
\hfill\break
a. Which variables from mpg dataset are categorical?
answer - The manufacturer, model, trans, drv, fl, class are the categorical variables of mpg data set.

\hfill\break
b. Which are continuous variables?
answer - The dsipl, year, cyl, cty, and hwy are the continous variables of mpg data set.
\hfill\break
c. Plot the relationship between displ (engine displacement) and hwy(highway miles per gallon). 
Mapped it with a continuous variable you have identified in #5-b. What is its result? Why it produced such output?
answer - The data  graph shows the data set of hwy,cyt and displ. 

```{r, error=TRUE}
ggplot(mpg, aes(x = cty, y = hwy, colour = displ)) + geom_point()
```
\hfill\break
9. Plot the relationship between displ (engine displacement) and hwy(highway miles per gallon) using geom_point(). Add a trend line over the existing plot 
using geom_smooth() with se = FALSE. Default method is “loess”.

```{r, error=TRUE}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) +
  geom_point(mapping=aes(color=class)) +
  geom_smooth(se = FALSE)
```
\hfill\break
10. Using the relationship of displ and hwy, add a trend line over existing 
plot. Set these = FALSE to remove the confidence interval and method = lm to 
check for linear modeling.

```{r, error=TRUE}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy, color = class)) +
  geom_point() +
  geom_smooth(se = FALSE, method = lm)
```
