---
title: "Rworksheet#4"
author: "JR Delgado"
date: "2022-11-22"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
\hfill\break

Worksheet-4 in R
Worksheet for R Programming
\hfill\break
------------------------------------------------------------------------
1. The table below shows the data about shoe size and height. 
   Create a data frame...
```{r, error=TRUE}

daframe <- data.frame(shoesize = c(6.5,9.0,8.5,8.5,10.5,7.0,9.5,9.0,13.0,7.5,10.5,8.5,12.0,10.5,13.0,11.5,8.5,5.0,10.0,6.5,7.5,8.5,10.5,8.5,10.5,11.0,9.0,13.0),
                      height = c(66.0,68.0,64.5,65.0,70.0,64.0,70.0,71.0,72.0,64.0,74.5,67.0,71.0,71.0,77.0,72.0,59.0,62.0,72.0,66.0,64.0,67.0,73.0,69.0,72.0,70.0,69.0,70.0), 
                      gender = c("F","F","F","F","M","F","F","F","M","F","M","F","M","M","M","M","F","F","M","F","F","M","M","F","M","M","M","M") )
daframe

names(daframe) <- list("Shoe size", "Height", "Gender")
daframe
```

\hfill\break
a. Describe the data. - The data shows the different shoe size among male and female in different heights.
\hfill\break
b. Find the mean of shoe size and height of the respondents.
Copy the codes and results.
Shoe size mean

```{r, error=TRUE}
mean(daframe$`Shoe size`)
```
height mean

```{r, error=TRUE}
mean(daframe$Height)
```
\hfill\break
c. Is there a relationship between shoe size and height?Why? Yes there is a relationship between shoe size and height, I can imagine that if your shoe size is large, you are also tall. The bigger the height, the taller the person is.

Using factor() 
examples

```{r, error=TRUE} 
Gender <- c("M","F","F","M")
factor_Gender <- factor(Gender)
factor_Gender
```
\hfill\break
2. Construct character vector months to a factor with factor() and assign the result to factor_months_vector. Print out factor_months_vector and assert that R prints out the factor levels below the actual values.

```{r, error=TRUE}
vector_months <- c("March","April","January","November","January","September","October","September","November","August","January","November","November","February","May","August","July","December","August","August","September","November","February","April")

factor_months_vector <- factor(vector_months)
factor_months_vector 
```
\hfill\break
3. Then check the summary() of the months_vector and factor_months_vector. 
Interpret the results of both vectors. Are they both equally useful in this case? 

```{r, error=TRUE}

summary(vector_months)
summary(factor_months_vector)
```
\hfill\break
4. Create a vector and factor for the table below.

```{r, error=TRUE}
factor_data <- c("East" = '1', "West" = '4', "North" = '3')
factor_data

new_order_data <- factor(factor_data,levels = c("East" = '1',  "West" = '4',  "North" = '3'))
print(new_order_data)
```
\hfill\break
5. Enter the data below in Excel with file name = import_march.csv
a. Import the excel file into the Environment Pane using read.table() function.
Write the code.
```{r, error=TRUE}
install.packages("readxl")
getwd()

setwd("/cloud/project/Rworksheet#4")
```


```{r, error=TRUE}

import <- read.table("import_march.csv", header = T, sep = ",")
import
```
\hfill\break
#b. View the dataset. Write the code and its result.
```{r, error=TRUE}

View(import)
```

