---
title: "Rworksheet#7a_Delgado"
author: "JR Delgado"
date: "2022-12-13"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


\hfill\break
Worksheet-7a in R
R Statistics
Worksheet for R Programming


\hfill\break
Basic Statistics
1. Create a data frame for the table below.
```{r, error=TRUE}
students <- c(1:10) 
Pre_test <- c(55,54,47,57,51,61,57,54,63,58)
post_test <- c(61,60,56,63,56,63,59,56,62,61)
data_frame <- data.frame(
  students , 
  Pre_test ,
  post_test )
data_frame
```

\hfill\break
```{r, error=TRUE}
colnames(data_frame) <- c("Students", "Pre-test","Post-test")
data_frame
```


\hfill\break
a. Compute the descriptive statistics using different 
#Write the codes and its result.
```{r, error=TRUE}
library(Hmisc)
library(pastecs)

describe(data_frame)

stat.desc(data_frame)
```


\hfill\break
2. The Department of Agriculture was studying the effects of several levels of a
`fertilizer on the growth of a plant. For some analyses, it might be useful to convert the fertilizer levels to an
ordered factor.

```{r, error=TRUE}
Dept_agriculture <- c(10,10,10, 20,20,50,10,20,10,50,20,50,20,10)
Dept_agriculture
```


\hfill\break
a. Write the codes and describe the result.
```{r, error=TRUE}
sorted1 <- sort(Dept_agriculture, decreasing = FALSE)
sorted1
```

 answer - The data show in ordered from lowest to highest
\hfill\break
3. Abdul Hassan, president of Floor Coverings Unlimited, has asked you to study the exercise levels undertaken by 10 subjects were “l”, “n”, “n”, “i”, “l” , “l”, “n”, “n”, “i”, “l” ; n=none, l=light, i=intense n=none, l=light, i=intense

```{r, error=TRUE}
n <- c("l", "n", "n", "i", "l" ,
       "l", "n", "n", "i", "l" )
```


\hfill\break
a. What is the best way to represent this in R? answer- Data Frame

```{r, error=TRUE}
subs <- data.frame(n)
subs 
```


\hfill\break
4. Sample of 30 tax accountants from all the states and territories of Australia and their individual state of origin is specified by a character vector of state mnemonics
 as:
 
```{r, error=TRUE}
state <- c("tas", "sa", "qld", "nsw", "nsw", "nt", "wa", "wa", "qld",
           "vic", "nsw", "vic", "qld", "qld", "sa", "tas", "sa", "nt",
           "wa", "vic", "qld", "nsw", "nsw", "wa", "sa", "act", "nsw",
           "vic", "vic", "act")
state
```



\hfill\break
 a. Apply the factor function and factor level. Describe the results.
 
```{r, error=TRUE}
fl <- factor(state)
fl
```


\hfill\break
5. From #4 - continuation:#• Suppose we have the incomes of the same tax accountants in another vector

```{r, error=TRUE}
incomes <- c(60, 49, 40, 61, 64, 60, 59, 54,
             62, 69, 70, 42, 56, 61, 61, 61, 58, 51, 48,
             65, 49, 49, 41, 48, 52, 46, 59, 46, 58, 43)
incomes
```


\hfill\break
a. Calculate the sample mean income for each state we can now use the special
function tapply():

```{r, error=TRUE}
apply1 <- tapply(state,incomes, mean)
apply1
```


\hfill\break
6. Calculate the standard errors of the state income means (refer again to number 3)

```{r, error=TRUE}
stdError <- function(x) sqrt(var(x)/length(x))
stdError(n)
incster <- tapply(incomes, state, stdError)
```


\hfill\break
a. What is the standard error? Write the codes.
  answer: NA

b. Interpret the result.
answer: the result is unavailable.The standard error cannot be determined.


\hfill\break
7. Use the titanic dataset.

```{r, error=TRUE}
data("Titanic")
head<- data.frame(Titanic)
```


\hfill\break
a. subset the titatic dataset of those who survived and not survived.
Show the codes and its result.

```{r, error=TRUE}
titanic1 <- subset(head, select = "Survived")
titanic1
```


\hfill\break

8. The data sets are about the breast cancer Wisconsin. The samples arrive periodically
 as Dr. Wolberg reports his clinical cases. The database therefore reflects this
 chronological grouping of the data. You can create this dataset in Microsoft Excel.

answer: The dataset is all about Breast Cancer.


\hfill\break

b. Import the data from MS Excel. Copy the codes.


```{r, error=TRUE}

library(readxl)
data <- read_excel("/cloud/project/Rworksheet7a/Breast_Cancer.xlsx")

data
```


\hfill\break
c. Compute the descriptive statistics using different packages. Find the values of:
c.1 Standard error of the mean for clump thickness.
```{r, error=TRUE}
clump1 <- length(data$`CL. thickness`)
clump2 <- sd(data$`CL. thickness`)
clump3 <- clump1/sqrt(data$`CL. thickness`)
clump3
```


\hfill\break
c.2 Coefficient of variability for Marginal Adhesion.
```{r, error=TRUE}
marginal_adhension <- sd(data$`Marg. Adhesion`) / mean(data$`Marg. Adhesion`)* 100
marginal_adhension
```


\hfill\break
c.3 Number of null values of Bare Nuclei.
```{r, error=TRUE}
Bare_Nuclei <- subset(data,`Bare. Nuclei` == "NA")
Bare_Nuclei
```


\hfill\break
c.4 Mean and standard deviation for Bland Chromatin
```{r, error=TRUE}
mean(data$`Bl. Cromatin`)
sd(data$`Bl. Cromatin`)
```


\hfill\break
c.5 Confidence interval of the mean for Uniformity of Cell Shape
```{r, error=TRUE}
cell_shape <- mean(data$`Cell Shape`)
cell_shape
```


\hfill\break
Calculate the mean
```{r, error=TRUE}
calmean <- mean(data$`Cell Shape`)
calmean
```


\hfill\break
Calculate the standard error of the mean
```{r, error=TRUE}
se1 <- length(data$`Cell Shape`)
se2 <- sd(data$`Cell Shape`)
se3 <- se2/sqrt(se1)
se3
```


\hfill\break

Find the t-score that corresponds to the confidence level

```{r, error=TRUE}
tscore = 0.05
tse = se1 - 1
cl = qt(p = tscore/ 2, df = tse,lower.tail = F)
cl
```


\hfill\break
Constructing the confidence interval
```{r, error=TRUE}
ci <- cl * se3
```


\hfill\break
Lower
```{r, error=TRUE}
lower <- calmean - ci
```


\hfill\break
Upper
```{r, error=TRUE}
upp <- calmean + ci
```


\hfill\break
d. How many attributes?
```{r, error=TRUE}
attributes(data)
```


\hfill\break
e. Find the percentage of respondents who are malignant. Interpret the results.
answer: There 18 respondents who are malignant
answer: There are total of 49 respondents.
```{r, error=TRUE}
percentage <- subset(data, Class == "malignant")
percentage
```


\hfill\break
9. Export the data abalone to the Microsoft excel file. Copy the codes.
```{r, error=TRUE}
install.packages("AppliedPredictiveModeling")
library("AppliedPredictiveModeling")
data("abalone")
View(abalone)
head(abalone)
summary(abalone)
```


\hfill\break
Exporting the data abalone to the Microsoft excel file
```{r, error=TRUE}
install.packages("xlsxjars")
install.packages("xlsx")
library(xlsx)
write.xlsx(abalone, "abalone.xlsx")
```
